Restructuring Data for Exascale Scientific Productivity

### 2016-03-02 papers/2016-Supercomputing/paper.tex
added notes on pland and progress

>>>>

COMPLETED WORK:\\
1. XGC1 ADIOS write to VisIt read, 3/5, 4/4, 2/6 split (4/4 converts the 4 double bytes to a proper float). Output is written to disk and read is directly. DataSpaces to do still. all scalars are written to both files.\\
2. Can we do this to Integers too?\\
3. XGC1 interpolation uses every 4th element only and did 3/5 split\\
4. Hasan to talk with Jeremy about how to make the interpolation work properly.
5. Doing off the particles for the first pass. Checking to see if they can use the fields instead.\\
6. Also measure the diff with the viz and the numerical eval for the 3/5 split\\
7. Make it neutral in terms of tech used to make double blind possible. Add in
the rest of the details once accepted\\
